### 2015-06-19 article/article.tex
started working more on the article, added lots of refs

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\newpage
\section*{Materials and Methods}
\subsection*{Theoretical foundation: location theory}
The idea of minimizing the sum of pairwise distance between objects is not new.
This has been investigated in location theory, with the goal of assigning position
to factories for example.

@@

\paragraph{Distance functions}

\subparagraph{Tree Indel distance on base pair tree}

RNA secondary structure is represented as a tree, where nodes are base pairs and unpaired positions are ignored.

\subparagraph{String Edit Distance}
%\subsection*{}

@@

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005
%
%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
%
%\end{thebibliography}

>>>>

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis"
\newpage
\section*{Methods}

\subsection*{Simple Tree Distance for Secondary Structure}

\paragraph{Base Pair Tree Representation}
% base pair tree representation vs abstract shapes
% upsides and downsides of the
% representation compared to abstract shape
RNA secondary structure can represented by base pair trees, where only base pairs are considered. This representation is very similar to level 3 RNA abstract shape \cite{abstract_shapes}, albeit the stem length information is conserved.
Although this representation greatly increases the size of the auxiliary space (codomain) compared to level 3 abstract shapes, it doesn't suffer from major changes in representation if small stem-loops are added or removed. It also doesn't map structures of widely varying stem length to the same element in the codomain.

%example of the conversion process 
\noindent The mapping from a Vienna dot bracket representation can be made simply by removing the dots (unpaired nucleotides) and then creating a tree from it. Since all nodes represent base pairs, the resulting tree can be considered unlabelled. Note that an artificial root is added to all trees.

\paragraph{Unit Tree Indel Distance}
% relation to the tree edit distance (special scoring scheme)
The unit tree indel distance is a simple and intuitive distance function based on the well known tree edit distance \cite{tai, zhang_shasha}, where insertions and deletions have a unit cost. Since it is applied to base pair trees which are unlabelled, node relabelling comes at no cost.

% interpretation of a score
\noindent Using this scoring scheme, a distance of $n$ means that the smallest number of base pair breakage or formation to transition from a base pair tree to another is $n$. The distance function retains the metric properties.

\subsection*{Optimization goal}

The idea of minimizing the sum of pairwise distance between sets of objects if far from new and a significant body of work has been done in the field of location theory \cite{compact_location}.

MC-Cons is a two-step optimization process relying on the minimization of the sum of pairwise distance of two distance functions. First, the

@@

@@

\section*{References}
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
% 
%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005
%
%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
%
%\end{thebibliography}

\begin{thebibliography}{10}
\bibitem{abstract_shapes}
Giegerich, Robert and Vo{\ss}, Bj\"{o}rn and Rehmsmeier, Marc. Abstract shapes
    of RNA. Nucleic Acids Research, 32(16):4843–4851, January 2004.

\bibitem{tai}
Kuo-Chung Tai. 1979. The Tree-to-Tree Correction Problem. J. ACM 26, 3 (1979), 422-433.

\bibitem{zhang_shasha}
Dennis Shasha and Kaizhong Zhang. Fast algorithms for the unit cost
    editing distance between trees. Journal of Algorithms, 11(4):581–621,
    December 1990.

\bibitem{compact_location}
 S. O. Krumke, M. V. Marathe, H. Noltemeier, et al. Compact location problems Theoretical Computer Science, Vol. 181, No. 2. (1997), pp. 379-404
\end{thebibliography}
